Seasonality in governing dynamics at submesoscales

### 2016-06-11 writeup/rocha_etal.tex
Fixes typos.

\keypoints{\item  Upper-ocean submesoscale (10-100 km) turbulence and inertia-gravity waves
                  undergo strong seasonal cycles that are out-of-phase.
           \item  Submesoscale turbulence dominates the horizontal velocity and
                  sea-surface height variability in late Winter/early Spring.
            \item Inertia-gravity waves dominate the the horizontal velocity and
                   sea-surface height variability in late Summer/early Fall.
                  }

@@

The seasonal cycle of the horizontal divergence, however, showcases the complexity
of the upper-ocean annual variability. If submesoscale eddies and fronts dominated
the near-surface variability all year, then the seasonal cycle of horizontal divergence,
vertical vorticity, and lateral strain rate would be in phase \citep[e.g.,][]{sasaki_etal2014}.
While there is a clear wintertime peak in divergence of daily-averaged velocity
(see dashed lines in figure \ref{fig2}a; RMS divergence $\sim$0.22 f in the 1/48$^\circ$
simulation), the hourly fields show
a stronger enhancement of
lateral divergence in late Summer/early Fall (RMS divergence $\sim$0.22 f the 1/48$^\circ$
simulation). Because the 1/48$^\circ$ simulation better resolve
smaller-scale submesoscale flows, the
winter peak in divergence is nearly as strong the summertime's. Of course, part of
these submesoscale fronts and eddies evolve relatively fast and there is no clear
temporal and spatial scale separation between those motions and inertia-gravity waves
\citep{mcwilliams2016}:
daily-averaging the velocity fields efficiently suppresses the summertime horizontally
divergent flows, but also reduces the wintertime lateral divergence by about 50$\%$.
As for the vorticity and strain rate, most of the lateral divergence is associated
with submesoscale flows: smoothing the the velocity fields with a 100km-cut-off
suppresses more than 80$\%$ of the RMS divergence.

>>>>

\keypoints{\item  Upper-ocean submesoscale (10-100 km) turbulence and inertia-gravity waves
                  undergo strong seasonal cycles that are out-of-phase.
           \item  Submesoscale turbulence dominates the horizontal velocity and
                  sea-surface height variability in late Winter/early Spring.
            \item Inertia-gravity waves dominate the horizontal velocity and
                   sea-surface height variability in late Summer/early Fall.
                  }

@@

The seasonal cycle of the horizontal divergence, however, showcases the complexity
of the upper-ocean annual variability. If submesoscale eddies and fronts dominated
the near-surface variability all year, then the seasonal cycle of horizontal divergence,
vertical vorticity, and lateral strain rate would be in phase \citep[e.g.,][]{sasaki_etal2014}.
While there is a clear wintertime peak in divergence of daily-averaged velocity
(see dashed lines in figure \ref{fig2}a; RMS divergence $\sim$0.22 f in the 1/48$^\circ$
simulation), the hourly fields show
a stronger enhancement of
lateral divergence in late Summer/early Fall (RMS divergence $\sim$0.22 f the 1/48$^\circ$
simulation). Because the 1/48$^\circ$ simulation better resolve
smaller-scale submesoscale flows, the
winter peak in divergence is nearly as strong the summertime's. Of course, part of
these submesoscale fronts and eddies evolve relatively fast and there is no clear
temporal and spatial scale separation between those motions and inertia-gravity waves
\citep{mcwilliams2016}:
daily-averaging the velocity fields efficiently suppresses the summertime horizontally
divergent flows, but also reduces the wintertime lateral divergence by about 50$\%$.
As for the vorticity and strain rate, most of the lateral divergence is associated
with submesoscale flows: smoothing the velocity fields with a 100km-cut-off
suppresses more than 80$\%$ of the RMS divergence.
